---
title: "Lucas Lab 13"
author: "Lucas Brack"
date: "April 18, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)



```

#Does BMI effect life expectancy?
  This will help show what cause death world wide because BMI is how much body fat a person has. This will tell us if body fat percentage has an effect on life expectancy. The null hypothesis is that there is no effect. The alternative is that life expectancy is affected by BMI. I test this by doing a pemutation test.


```{r, results='hide',warning=F, message=FALSE}
bmi<-read_csv("Male_BMI.csv")%>%
  filter(Country=="United States" | Country=="Venezuela")%>%
  select(Country,`1980`:`2008`)%>%
  gather(`1980`: `2008`, key = year, value = BMI)
bmi
life_exp<-read_csv("Life_exP_at_birth.csv")%>%
  filter(`Life expectancy`=="United States" | `Life expectancy`=="Venezuela")%>%
  select("Life expectancy",`1980`:`2008`)%>%
  gather(`1980`: `2008`, key = year, value = Life_exp)
  colnames(life_exp)[1]<-"Country"
life_exp
col_mean <- function(df) {
  #Map function that return mean of a column
  output <- vector("double", length(df))
  for (i in seq_along(df)) {
    output[i] <- mean(df[[i]])
  }
  output
}
mean_bmi<-function(input){
  bmi1<-bmi%>%
  filter(Country==input)%>%
  select(BMI)
  bmi1
  return(bmi1)
}

mean_life_exp<-function(input){
  life_exp1<-life_exp%>%
  filter(Country==input)%>%
  select(Life_exp)
  life_exp1
  col_mean(life_exp1)
}
```

```{r,warning=F, message=FALSE}
bmi_mean=map_dbl(mean_bmi("United States"),mean)-map_dbl(mean_bmi("Venezuela"),mean)#Map function that calculates the mean for BMI
bmi_mean
mean_life_exp("United States")-mean_life_exp("Venezuela")
```

```{r, results='hide',warning=F, message=FALSE}
perm_mean <- function(perms = 1000, values, n1){
  ## Variables ##
  # perms: The number of permutations 
  # values (num): 
  # n1 (int): Size of group 1
  ###############
  
  # Step 1: Create vector of zeroes of length "perms" to store permuted mean differnces
  
  zero_vector=numeric(1000)
  
  # Loop throught number of permutations
  for (i in c(1:perms)){
    # Step 2:Randomly separate vector "values" into disjoint groups of size "n1" and "length(values) - n1" respectively
    groups<-sample(values,length(values), replace = FALSE)
    
    group1<-groups[1:n1]
    group2<-groups[1+n1:length(values)-1]
    
    # Step 3: Compute the sample means for the two groups from step 2
    mean_group1<-mean(group1)

    mean_group2<-mean(group2)
    
    # Step 4:  Compute the difference in sample means, store the value in the vector from step 1
    zero_vector[i]=(mean_group2-mean_group1)
  }
  return(zero_vector)
  
}
```

```{r, results='hide'}
mean_b<-enframe(perm_mean(perms = 1000, bmi$BMI, 10))
                
```

```{r,warning=F, message=FALSE}
bmi_mean
quantile(mean_b$value, c(.99))
```

```{r,warning=F, message=FALSE}

ggplot(data=mean_b)+
  geom_histogram(mapping = aes(x=value),fill="red")+
  geom_vline(xintercept=bmi_mean, color="blue")
```

The graph shows that data is in the 99.9%tile, which means that there is a life expectancy is affected by BMI, which makes the null hypothesis incorrect. Since the United States has a higher BMI and life expectancy, this means the countries with higher average BMI should have a higher life expectancy.